---
title: "Hearth Science"
author: "Xue Zou"
date: "May 1, 2016"
output: html_document
---

## Intrduction to Hearth Stone Card Game

XXXXXX


## Exploratory 
load library 
```{r pressure, echo=FALSE}
setwd("~/Desktop/final/")
#rm(list=ls()) 
library(knitr)
opts_chunk$set(cache = TRUE, message = FALSE)
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(gridExtra)
library(graphics)
library(plotrix)
library(gridBase)
library(grid)
library(sqldf)
library(ggrepel)
library(scales)
theme_set(theme_bw(base_size = 16))
```
load data
```{r}
load("minions_text.RData")
data<-minions_text
```
distribution of Cost
```{r}
#remove costs that are "12" and "20" 
Cost<-data%>%dplyr::arrange(cost)
Cost<-unique(data%>%filter(cost<=10)%>%group_by(cost)%>%mutate(n=n())%>%ungroup()%>%select(cost,n))
Cost<-Cost%>%mutate(pos=cumsum(n)-n/2)
p<-Cost%>%ggplot(aes(x=1,y=n,fill=factor(cost)))
p+geom_bar(stat="identity",width=1)+geom_text(aes(x=1.6,y=pos,label = percent(n/sum(n))))+coord_polar(theta="y")+ xlab('')+ylab('')+theme(axis.text=element_blank(),axis.ticks=element_blank(),panel.grid=element_blank())+ggtitle("Pie Chart of Card Cost")
#pie(slices,labels = lbls, col=rainbow(length(lbls)),main="Pie Chart of Card Cost distribution")
#histogram
qplot(data$cost,geom="histogram",xlab="cost",main="Histogram for cost")
```

Conclusion: cards with cost "2","3","4" out of the 11 possible costs occupying around 54% in total are most common in the deck

distribution of attack
```{r}
Attackk<-data%>%arrange(attack)
Attack<-unique(Attackk%>%group_by(attack)%>%mutate(n=n())%>%ungroup()%>%select(attack,n))
#pie chart
Attack<-Attack%>%mutate(pos=cumsum(n)-n/2)
p<-Attack%>%ggplot(aes(x=1,y=n,fill=factor(attack)))
p+geom_bar(stat="identity",width=1)+geom_text(aes(x=1.6,y=pos,label = percent(n/sum(n))))+coord_polar(theta="y")+ xlab('')+ylab('')+theme(axis.text=element_blank(),axis.ticks=element_blank(),panel.grid=element_blank())+ggtitle("Pie Chart of Attack")
#histogram
qplot(data$attack,geom="histogram",xlab="attack",main="Histogram for attack")
```

distribution of health
```{r}
Health<-data%>%arrange(health)
Health<-unique(Health%>%group_by(health)%>%mutate(n=n())%>%ungroup()%>%select(health,n))
#pie chart
Health<-Health%>%mutate(pos=cumsum(n)-n/2)
p<-Health%>%ggplot(aes(x=1,y=n,fill=factor(health)))
p+geom_bar(stat="identity",width=1)+geom_text(aes(x=1.6,y=pos,label = percent(n/sum(n))))+coord_polar(theta="y")+ xlab('')+ylab('')+theme(axis.text=element_blank(),axis.ticks=element_blank(),panel.grid=element_blank())+ggtitle("Pie Chart of Health")
#histogram
qplot(data$health,geom="histogram",xlab="health",main="Histogram for health")
```

distribution of mechanics 
```{r}
Mechanics<-data%>%arrange(mechanics)
Mechanics<-unique(Mechanics%>%group_by(mechanics)%>%mutate(n=n())%>%ungroup()%>%select(mechanics,n))
#pie chart
Mechanics<-Mechanics%>%mutate(pos=cumsum(n)-n/2)
p<-Mechanics%>%ggplot(aes(x=1,y=n,fill=factor(mechanics)))
p+geom_bar(stat="identity",width=1)+geom_text(aes(x=1.6,y=pos,label = percent(n/sum(n))))+coord_polar(theta="y")+ xlab('')+ylab('')+theme(axis.text=element_blank(),axis.ticks=element_blank(),panel.grid=element_blank())+ggtitle("Pie Chart of Mechanics")
#histogram
library(ggplot2)
qplot(data$mechanics,,xlab="mechanics",main="Histogram for Mechanics")+theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

distribution of playerclass
```{r}
pc<-data%>%arrange(playerClass)
pc<-unique(pc%>%group_by(playerClass)%>%mutate(n=n())%>%ungroup()%>%select(playerClass,n))
#pie chart
playerClass<-pc%>%mutate(pos=cumsum(n)-n/2)
p<-playerClass%>%ggplot(aes(x=1,y=n,fill=factor(playerClass)))
p+geom_bar(stat="identity",width=1)+geom_text(aes(x=1.6,y=pos,label = percent(n/sum(n))))+coord_polar(theta="y")+ xlab('')+ylab('')+theme(axis.text=element_blank(),axis.ticks=element_blank(),panel.grid=element_blank())+ggtitle("Pie Chart of playerClass")
#histogram
library(ggplot2)
qplot(data$playerClass,,xlab="playerClass",main="Histogram for playerClass")+theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

distribution of cardSet
```{r}
cs<-data%>%arrange(cardSet)
cs<-unique(cs%>%group_by(cardSet)%>%mutate(n=n())%>%ungroup()%>%select(cardSet,n))
#pie chart
cs<-cs%>%mutate(pos=cumsum(n)-n/2)
p<-cs%>%ggplot(aes(x=1,y=n,fill=factor(cardSet)))
p+geom_bar(stat="identity",width=1)+geom_text(aes(x=1.6,y=pos,label = percent(n/sum(n))))+coord_polar(theta="y")+ xlab('')+ylab('')+theme(axis.text=element_blank(),axis.ticks=element_blank(),panel.grid=element_blank())+ggtitle("Pie Chart of cardSet")
#histogram
library(ggplot2)
qplot(data$cardSet,,xlab="cardSet",main="Histogram for cardSet")+theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

distribution of rarity
```{r}
rr<-unique(data%>%group_by(rarity)%>%mutate(n=n())%>%ungroup()%>%select(rarity,n))
#pie chart
rr<-rr%>%mutate(pos=cumsum(n)-n/2)
p<-rr%>%ggplot(aes(x=1,y=n,fill=factor(rarity)))
p+geom_bar(stat="identity",width=1)+geom_text(aes(x=1.6,y=pos,label = percent(n/sum(n))))+coord_polar(theta="y")+ xlab('')+ylab('')+theme(axis.text=element_blank(),axis.ticks=element_blank(),panel.grid=element_blank())+ggtitle("Pie Chart of rarity")
#histogram
library(ggplot2)
qplot(data$cardSet,,xlab="rarity",main="Histogram for rarity")+theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

##correlation of warlock

#pearson correlation of cards
load library
```{r}
library(cowplot)
library(rvest)
library(XML)
library(Heatplus)
library(vegan)
library(RColorBrewer)
library(gplots) 
library(devtools)
library(reshape)
library(dendextend)
library(colorspace)
library(reshape2)
```
load data
```{r}
baseURL<-"http://www.hearthstonetopdecks.com/deck-category/class/warlock/page/"
classes<-c("druid/","hunter/","mage/","paladin/","priest/","rogue/","shaman/","warlock/","warrior/")
tableURL<-"http://www.hearthstonetopdecks.com/deck-category/class/druid/page/"

```

data wrangling 
```{r}
allDecks<-list()

for (j in 1:5){
  tableURL<-paste(baseURL,j,sep="")
  tables<-as.data.frame(readHTMLTable(tableURL))
  deckNames<-lapply(tables[,2],as.character)
  deckNames<-unlist(deckNames)
  
  for(i in 1:length(deckNames)){
    urlName<-tolower(gsub("\\s","-",gsub("[^\\w \\s]+","",deckNames[i],perl = TRUE),perl = TRUE))
    
    testURL<-paste("http://www.hearthstonetopdecks.com/decks/",urlName,sep="")
    tryCatch(webpage<-read_html(testURL),error=function(e){return(i)})
    
    cardNames<-webpage%>%
      html_nodes(".card-name")%>%
      html_text()
    
    cardCounts<-webpage%>%
      html_nodes(".card-count")%>%
      html_text()%>%
      as.numeric()
    
    deckId<-(j-1)*25+i
    
    deck<-cbind(cardNames,cardCounts,rep(deckId,length(cardNames)))
    
    allDecks[[deckId]]<-deck
  }
}

largerTable<-data.frame()

for (i in 8:125){
  largerTable<-rbind(largerTable,allDecks[[i]])
}

largerTable<-largerTable%>%spread(key=V3,value=cardCounts)

for (i in 2:length(largerTable)){
  largerTable[,i]<-as.numeric(as.character(largerTable[,i]))
}

largerTable[is.na(largerTable)]<-0

rownames(largerTable)<-t(largerTable[,1])

```

dataset as a whole
```{r}
###
data<-largerTable%>%select(-cardNames)
data.t<-t(data)
d1<-dist(data) 
d2<-dist(data.t)
cormat<-round(cor(data.t),2)
mtscaled<-as.matrix(d1)
#correlation
cor_data<-round(cor(data.t),2)
data.m<-melt(cor_data)
##############hierarchical culsutering 
hClust<-hclust(dist(data),method="complete")
plot(hClust,cex=1)
```

heatmap
```{r}

heatmap(mtscaled,Colv=F,cexRow=0.4,cexCol = 0.4)
#data exploration ( 260 CV)
image(as.matrix(d1))
library(ggplot2)
#no label of x-axis, y-axis
ggplot(data = data.m, aes(x=X1, y=X2, fill=value)) + 
  geom_tile()

qplot(x=X1, y=X2, data=data.m, fill=value, geom="tile") + scale_fill_gradient2(limits=c(-1, 1))
#################################################
#compute the correlation matrix
cor_data.t<-round(cor(data.t),2)
head(cor_data.t)
melted_data.t <- melt(cor_data.t)
head(melted_data.t)
ggplot(data = melted_data.t, aes(x=X1, y=X2, fill=value)) + 
  geom_tile()
#get the lower and upper triangles of the correlation matrix
# Get lower triangle of the correlation matrix
  get_lower_tri<-function(data.t){
    data.t[upper.tri(data.t)] <- NA
    return(data.t)
  }

  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(data.t){
    data.t[lower.tri(data.t)]<- NA
    return(data.t)
  }
upper_tri <- get_upper_tri(data.t)
upper_tri

# Melt the correlation matrix
melted_data.t <- melt(upper_tri, na.rm = TRUE)

# Heatmap
p<-ggplot(data = melted_data.t, aes(X2, X1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
  theme_minimal()

p+ theme(axis.text.y = element_text(vjust = 1, 
    size = 8, hjust = 1))+theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 8, hjust = 1))+ scale_x_discrete(expand = c(0, 0)) + scale_y_discrete(expand = c(0, 0)) 


```

#new selection of cards (filtering) 
```{r}
###HC
hClust<-hclust(dist(largerTable),method="complete")
plot(hClust,cex=0.6)

set.seed(1111)
###PCA
cormat=cor(data.t)
pc<-prcomp(cormat)
summary(pc)

pcaData <-pc$x[,1:2]
pca1 <-pc$x[,1]
pca2 <-pc$x[,2]

wss <- (nrow(pcaData)-1)*sum(apply(pcaData,2,var))
for (i in 2:15) wss[i] <- sum(kmeans(pcaData,centers=i)$withinss)
plot(1:15, wss, type="b", xlab="Number of Clusters",
     ylab="Within groups sum of squares")

###distance matrix 
d<-dist(largerTable)
mtscaled<-as.matrix(d)
image(mtscaled)
heatmap(mtscaled,Colv=F,cexRow=0.4,cexCol = 0.4)
#correlation matrix 
melted_cormat <- melt(cormat)
p<-ggplot(data = melted_cormat, aes(X2, X1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
  theme_minimal()

p+ theme(axis.text.y = element_text(vjust = 1, 
    size = 6, hjust = 1))+theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1))+scale_x_discrete(expand = c(0, 0)) + scale_y_discrete(expand = c(0, 0))+theme(legend.background=element_rect(),legend.margin=unit(1,"cm"))

### triangle heatmap
install.packages("GGally")
source("https://raw.githubusercontent.com/briatte/ggcorr/master/ggcorr.R")
ggcorr(cormat)
ggcorr(data=NULL,cor_matrix=cor(data.t,use = "everything"),nbreak=4,low = "steelblue", mid = "white", high = "darkred")
ggcorr(data=NULL,cor_matrix=cor(data.t,use = "everything"),nbreak=4,palette = "RdGy")
ggcorr(cormat,hjust = 0.75, size = 5, color = "grey50")


#qplot(x=pc$x[,1],y=pc$x[,2], geom = "jitter" , color=class, xlab="PC1", ylab = "PC2")
tmp <- data.frame(pc$rotation, name = rownames(data))
tmp %>%  ggplot(aes(PC1, PC2)) + geom_point() + 
  geom_text_repel(aes(PC1, PC2, label=name),
                  data = filter(tmp,PC1 < -0.15 | PC1 >0.2 | PC2 < -0.2 | PC2>0.1))

```

#look at 4 clusters
```{r}
kmeans.cluster<-kmeans(pcaData, centers=4)
pc.df<-data.frame(ID=names(pca1),PCA1=pca1, PCA2=pca2, 
                  Cluster=factor(kmeans.cluster$cluster))
### seperate data set
fullcluster<-pc.df%>%select(-PCA1,-PCA2)
cluster1<-fullcluster%>%filter(Cluster=="1")%>%select(-Cluster)
cluster2<-fullcluster%>%filter(Cluster=="2")%>%select(-Cluster)
cluster3<-fullcluster%>%filter(Cluster=="3")%>%select(-Cluster)
cluster4<-fullcluster%>%filter(Cluster=="4")%>%select(-Cluster)
#conver the rownames to first column "ID"
ID<-rownames(data)
rownames(data)<-NULL
data<-cbind(ID,data)
#create 4 dataset by "ID"
dataset1<-dplyr::right_join(data,cluster1,by="ID")
dataset2<-dplyr::right_join(data,cluster2,by="ID")
dataset3<-dplyr::right_join(data,cluster3,by="ID")
dataset4<-dplyr::right_join(data,cluster4,by="ID")

#convert the first column to rownames
rownames(dataset1)<-dataset1$ID
rownames(dataset2)<-dataset2$ID
rownames(dataset3)<-dataset3$ID
rownames(dataset4)<-dataset4$ID
dataset1<-dataset1[,-1]
dataset2<-dataset2[,-1]
dataset3<-dataset3[,-1]
dataset4<-dataset4[,-1]
data1.t<-t(dataset1)
data2.t<-t(dataset2)
data3.t<-t(dataset3)
data4.t<-t(dataset4)
#correlation within the first dataset
cormat1<-round(cor(data1.t),2)
cormat2<-round(cor(data2.t),2)
cormat3<-round(cor(data3.t),2)
cormat4<-round(cor(data4.t),2)
# HC of the first dataset
hClust1<-hclust(dist(dataset1),method="complete")
hClust2<-hclust(dist(dataset2),method="complete")
hClust3<-hclust(dist(dataset3),method="complete")
hClust4<-hclust(dist(dataset4),method="complete")
plot(hClust1,cex=0.6)
plot(hClust2,cex=0.6)
plot(hClust3,cex=0.6)
plot(hClust4,cex=0.6)

#correlation matrix 
melted_cormat1 <- melt(cormat1)
p1<-ggplot(data = melted_cormat1, aes(X2, X1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_minimal()

p1+ theme(axis.text.y = element_text(vjust = 1, 
                                    size = 10, hjust = 1))+theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                                                                            size = 10, hjust = 1))+scale_x_discrete(expand = c(0, 0)) + scale_y_discrete(expand = c(0, 0))+theme(legend.background=element_rect(),legend.margin=unit(1,"cm"))

melted_cormat2 <- melt(cormat2)
p2<-ggplot(data = melted_cormat2, aes(X2, X1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_minimal()

p2+ theme(axis.text.y = element_text(vjust = 1, 
                                    size = 10, hjust = 1))+theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                                                                            size = 10, hjust = 1))+scale_x_discrete(expand = c(0, 0)) + scale_y_discrete(expand = c(0, 0))+theme(legend.background=element_rect(),legend.margin=unit(1,"cm"))


melted_cormat3 <- melt(cormat3)
p3<-ggplot(data = melted_cormat3, aes(X2, X1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_minimal()

p3+ theme(axis.text.y = element_text(vjust = 1, 
                                    size = 10, hjust = 1))+theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                                                                            size = 10, hjust = 1))+scale_x_discrete(expand = c(0, 0)) + scale_y_discrete(expand = c(0, 0))+theme(legend.background=element_rect(),legend.margin=unit(1,"cm"))


melted_cormat4 <- melt(cormat4)
p4<-ggplot(data = melted_cormat4, aes(X2, X1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_minimal()

p4+ theme(axis.text.y = element_text(vjust = 1, 
                                    size = 10, hjust = 1))+theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                                                                            size = 10, hjust = 1))+scale_x_discrete(expand = c(0, 0)) + scale_y_discrete(expand = c(0, 0))+theme(legend.background=element_rect(),legend.margin=unit(1,"cm"))
```
