---
title: "Hearth-science"
output: html_document
---

# Simulation 1
Assumptions:
1. Players will not use the card with cost 0 in the earlier several turns.
2. Cost can roughly represent the value of the card, thus we can maximum the cost of all 30 cards to maximum the value.
3. We focus on the first 5 turns.

First, create decks with all reasonable combinations of small cards (1-5) and others.

```{r}
decks <- expand.grid(n1=0:6, n2=0:6, n3=0:6, n4=0:6, n5=0:6)
decks <- decks %>% tbl_df %>% mutate(others = 30-n1-n2-n3-n4-n5)

```

Next, use similation to estimate the probability to use card in the first 1/2/3/4/5-turn for each deck. Estimations are made for offensive player, as the defensive player has higher possiblity to use cards (4 cards at the begining with a special 0 cost card that temporatily increases the mana by 1) for the first few turns.

```{r,eval=FALSE}
prob_usecard <- function(deck){
        card <- rep(c(1,2,3,4,5,10), deck)
                
        # offensive player
        temp <- t(replicate(1000,sample(card,30)))
        # assume choosing the 3 smallest cards for the starting hand
        sortcard <- t(apply(temp[,1:6],1,sort))
        temp[,1:6] <- sortcard
        sortcard2 <- t(apply(temp[,4:30],1,function(x){sample(x,27)}))
        temp[,4:30] <- sortcard2
        rm(sortcard)
        rm(sortcard2)
        
        # p1: can use card in the first turn
        p1 <- mean(apply(temp[,1:4],1,function(c){as.numeric(sum(c<2)>0)}))  
        # p2: can use card in the first 2 turns
        p2 <- mean(apply(temp[,1:5],1,function(c){as.numeric(sum(c<3)>0)}))  
        # p3: can use card in the first 3 turns
        p3 <- mean(apply(temp[,1:6],1,function(c){as.numeric(sum(c<4)>0)}))  
        # p4: can use card in the first 4 turns
        p4 <- mean(apply(temp[,1:7],1,function(c){as.numeric(sum(c<5)>0)}))  
        # p5: can use card in the first 5 turns
        p5 <- mean(apply(temp[,1:8],1,function(c){as.numeric(sum(c<6)>0)}))  
        
        c(p1, p2, p3, p4, p5)     
}

# get the probability of using card and combine
usecard <- t(apply(decks,1,prob_usecard))
colnames(usecard) <- c("p1","p2","p3","p4","p5")
decks <- cbind(decks,usecard) %>% 
        # add the total cost for each deck
        mutate(sum = n1+2*n2+3*n3+4*n4+5*n5+10*others) 
rm(usecard)

# save simulation results 
write.csv(decks,file="/Users/Yinnan/Desktop/2016/HearthScience/simulation.csv")

library(readr)
# For loading from my own computer
# decks <- read_csv("/Users/Yinnan/Desktop/2016/HearthScience/simulation.csv") 
```


```{r}
library(ggplot2)
library(dplyr)
# get the simulation result from github
url <- "https://raw.githubusercontent.com/jihua0125/HearthScience/master/simulation.csv"
decks <- read_csv(url)

decks <- decks[,-1]

# constrain on probability of using card
decks.constrain <- decks %>% tbl_df %>% filter(p4>0.95, p2>0.5, p3>0.9, others>10) %>%
        arrange(desc(sum)) 

decks.constrain %>% summarize(min2 = min(n1+n2), min3 = min(n1+n2+n3), min4 = min(n1+n2+n3+n4))

# save constrain result
# write.csv(decks.constrain,file="/Users/Yinnan/Desktop/2016/HearthScience/simulation_constrain.csv")


```


# Simulation 2
For each deck, there are several "core" cards that can have the greatest effect when they are used together. We will usually put 2 cards for each component of core cards, and we want to get at least one for every component as early as possible.

First we list all possible decks with core cards and normal cards. Each set of core cards includes 2-5 different components.

```{r}
# sort the first 6 card for offensive side/early hand, assume we will always keep the core card
sort.offensive <- function(tmp){
        sortcard <- t(apply(tmp[,1:6],1,function(x){sort(x,decreasing = T)}))
        tmp[,1:6] <- sortcard
        sortcard2 <- t(apply(tmp[,4:30],1,function(x){sample(x,27)}))
        tmp[,4:30] <- sortcard2
        tmp
}

# 2 components core cards set, each with 2 cards
card <- c(1,1,2,2,rep(0,26))
tmp <- t(replicate(10000,sample(card,30)))

tmp <- sort.offensive(tmp)

# the probability of having the complete set of core cards by n turns
# we want to know the probability by each turn i

offen_core2 <- function(i){
        mean(apply(tmp[,1:(i+3)],1,function(c){as.numeric(sum(c==1)>0 & sum(c==2)>0)})) 
}

o2 <- sapply(1:27,offen_core2)



# 3 components core cards set, each with 2 cards
card <- c(1,1,2,2,3,3,rep(0,24))
tmp <- t(replicate(10000,sample(card,30)))

tmp <- sort.offensive(tmp)

# the probability of having the complete set of core cards by n turns
# we want to know the probability by each turn i
offen_core3 <- function(i){
        mean(apply(tmp[,1:(i+3)],1,function(c){as.numeric(sum(c==1)>0 & sum(c==2)>0 & sum(c==3)>0)})) 
}

o3 <- sapply(1:27,offen_core3)


# 4 components core cards set, each with 2 cards
card <- c(1,1,2,2,3,3,4,4,rep(0,22))
tmp <- t(replicate(10000,sample(card,30)))

tmp <- sort.offensive(tmp)

# the probability of having the complete set of core cards by n turns
# we want to know the probability by each turn i
offen_core4 <- function(i){
        mean(apply(tmp[,1:(i+3)],1,function(c){as.numeric(sum(c==1)>0 & sum(c==2)>0 & sum(c==3)>0) & sum(c==4)>0})) 
}

o4 <- sapply(1:27,offen_core4) 


# 5 components core card set
card <- c(1,1,2,2,3,3,4,4,5,5,rep(0,20))
tmp <- t(replicate(10000,sample(card,30)))

tmp <- sort.offensive(tmp)

# the probability of having the complete set of core cards by n turns
# we want to know the probability by each turn i
offen_core5 <- function(i){
        mean(apply(tmp[,1:(i+3)],1,function(c){as.numeric(sum(c==1)>0 & sum(c==2)>0 & sum(c==3)>0) & sum(c==4)>0 & sum(c==5)>0})) 
}

o5 <- sapply(1:27,offen_core5) 
```




Similarly we can estimate the probability for the defensive side/late hand.

```{r}
# sort the first 6 card for offensive side, assume we will always keep the core card
sort.defensive <- function(tmp){
        sortcard <- t(apply(tmp[,1:8],1,function(x){sort(x,decreasing = T)}))
        tmp[,1:8] <- sortcard
        sortcard2 <- t(apply(tmp[,5:30],1,function(x){sample(x,26)}))
        tmp[,5:30] <- sortcard2
        tmp
}

# 2 components core cards set, each with 2 cards
card <- c(1,1,2,2,rep(0,26))
tmp <- t(replicate(10000,sample(card,30)))

tmp <- sort.defensive(tmp)

# the probability of having the complete set of core cards by n turns
# we want to know the probability by each turn i

defen_core2 <- function(i){
        mean(apply(tmp[,1:(i+4)],1,function(c){as.numeric(sum(c==1)>0 & sum(c==2)>0)})) 
}

d2 <- sapply(1:26,defen_core2)



# 3 components core cards set, each with 2 cards
card <- c(1,1,2,2,3,3,rep(0,24))
tmp <- t(replicate(10000,sample(card,30)))

tmp <- sort.defensive(tmp)

# the probability of having the complete set of core cards by n turns
# we want to know the probability by each turn i
defen_core3 <- function(i){
        mean(apply(tmp[,1:(i+4)],1,function(c){as.numeric(sum(c==1)>0 & sum(c==2)>0 & sum(c==3)>0)})) 
}

d3 <- sapply(1:26,defen_core3)


# 4 components core cards set, each with 2 cards
card <- c(1,1,2,2,3,3,4,4,rep(0,22))
tmp <- t(replicate(10000,sample(card,30)))

tmp <- sort.defensive(tmp)

# the probability of having the complete set of core cards by n turns
# we want to know the probability by each turn i
defen_core4 <- function(i){
        mean(apply(tmp[,1:(i+3)],1,function(c){as.numeric(sum(c==1)>0 & sum(c==2)>0 & sum(c==3)>0) & sum(c==4)>0})) 
}

d4 <- sapply(1:26,defen_core4) 


# 5 components core card set
card <- c(1,1,2,2,3,3,4,4,5,5,rep(0,20))
tmp <- t(replicate(10000,sample(card,30)))

tmp <- sort.defensive(tmp)

# the probability of having the complete set of core cards by n turns
# we want to know the probability by each turn i
defen_core5 <- function(i){
        mean(apply(tmp[,1:(i+3)],1,function(c){as.numeric(sum(c==1)>0 & sum(c==2)>0 & sum(c==3)>0) & sum(c==4)>0 & sum(c==5)>0})) 
}

d5 <- sapply(1:26,defen_core5) 
```


```{r}
# show results

offensive <- data.frame(o2,o3,o4,o5)
colnames(offensive) <- c(2,3,4,5)
offensive <- offensive %>% mutate(turn=1:27, card=4:30) %>% gather("n_core","prob",1:4)

defensive <- data.frame(d2,d3,d4,d5)
colnames(defensive) <- c(2,3,4,5)
defensive <- defensive %>% mutate(turn=1:26, card=5:30) %>% gather("n_core","prob",1:4)


#pdf("~/Desktop/2016/HearthScience/corecard_simulation.pdf")

offensive %>% ggplot(aes(card,prob)) + geom_line(aes(color=n_core)) +
        ggtitle("The probability of getting the whole set of core cards (Offensive)") +
        scale_x_continuous(breaks=4:30) +
        scale_y_continuous(breaks=seq(0,1,0.1))
defensive %>% ggplot(aes(card,prob)) + geom_line(aes(color=n_core)) +
        ggtitle("The probability of getting the whole set of core cards (Defensive)") +
        scale_x_continuous(breaks=5:30) +
        scale_y_continuous(breaks=seq(0,1,0.1))
#dev.off()



```



